\LARGE \bf Blockchain for routing correctness?

### 2018-07-15 paper.tex
changed apostrophe

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
Border Gateway Protocol does not guarantee correctness of routing updates. A given routing update for prefix X is \textit{correct} if for every AS in the final AS-path the AS-path that was used to create the AS’s respective routing update is still the most recent and valid for destination prefix X. Since BGPsec and RPKI do not provide correctness, this paper explores Blockchain-Merkle BGP (BM-BGP) which uses of blockchain and indexed merkle trees to provide correctness within the time frame of consensus in a chosen consensus protocol. The indexed merkle structure analyzed does not scale well because merkle roots on the blockchain cannot be updated and still have previous merkle verification work without at least log2(N) hashes (where N is leaf nodes in tree) sent to each node trying to validate the correctness of a transaction. This paper only explores theory and does not test the protocol. Sample code for IP indexed merkle trees (code)

@@

Proof of correctness has 3 parts: integrity, identity, and currentness. RPKI and BGPsec (when implemented) provide full integrity, full identity, and partial currentness. In BGPsec, there is a timestamp, however, there it does no guarantee that a given routing update is the most recent one because updates can be withheld maliciously or from new filters []. An important property of Nakamoto consensus is the incentivization of data sharing, which eliminates many data availability problems. However, Nakamoto consensus is not scalable without 2nd layer solutions and traditional 2nd layer solutions cannot be used to help scaling the blockchain proposed in this paper.

\subsection{Shortcomings and Author’s Note}

There are several shortcomings in this draft. I (the author and researcher) am not confident in my ability to understand the severity of the data availability problem in BGP or any network relying on an external gateway protocol. I need guidance from an expert in BGP to (1) create a set of experiments to test the severity of data availability and (2) understand the current literature around data availability. Since it is one of the first iterations of this paper, I feel it is appropriate to add this disclaimer. I am much more confident in my understanding of blockchain than BGP. I am calling on those who are an expert in BGP to collaborate with me. Thank you.

@@

There are other attacks on blockchain: nothing at stake attack (for POS), sybil attacks, and quantum computers. Briefly, nothing at stake is the problem that block producers do not have any incentive to choose one block, and therefore, will mine after any block as long as they are confident that the blocks before the one they are mining will be accepted by the network. The worry is that miners will mine on top of forks in order to increase the likelihood of a payout, and this does not solve the double spend problem. Sybil attacks occur when malicious nodes cut of honest nodes from the network [Heilman 2015), but it is hard to successfully do if the P2P network is interconnected well (from good seeding). Quantum computers are only a problem if the signature algorithms that are used in transactions are based on the discrete log problem (RSA or ECC) because Shor’s algorithm makes it computationally feasible to factor large numbers (Shor 1994). Hash functions are not as vulnerable from quantum computers as signatures are because key sizes only have to be doubled.

@@

Now that there is an efficient tree the merkle root can be created. The tree is recursively hashed from bottom up. First, we must must make sure that every middle children has left and right siblings that are not None. Siblings are the other children of one’s parent. For each sibling slot that is none (for a middle node), we add a node with a data string ”LEFT” or ”RIGHT” because otherwise, middle node hashes could not be distinguished from left hashes if there are only a right and middle child. Now the merkle root can be created with integrity of position of the leaf nodes. We start at the root node, find the root’s hash by hashing each of its children, which we get by hashing their children, and so on until a leaf node is reached (base case of recursive function) and then we backtrack.

@@

Another advantage of a centralized trusted authority is that many ASes already have connections with ICANN and a RIR to some degree because of RPKI. It is probably easier to convince ASes to add a connection to their RIR than join a p2p network. Further, a central authority can fix a bug faster than a consensus protocol, although it may take longer to find the bug there are less parties running the software than in a consensus protocol. The main disadvantage to a central authority is that there is single weak point. If the trusted authoritys servers fail, there could be significant outages. This weakness can be mitigated through distributed and fault-tolerant computing. It is not clear whether an attack on an authority's servers is easier than the ripple consensus protocol (described in previous section) because ripple has a >20\% attack.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
Border Gateway Protocol does not guarantee correctness of routing updates. A given routing update for prefix X is \textit{correct} if for every AS in the final AS-path the AS-path that was used to create the AS’s respective routing update is still the most recent and valid for destination prefix X. Since BGPsec and RPKI do not provide correctness, this paper explores Blockchain-Merkle BGP (BM-BGP) which uses of blockchain and indexed merkle trees to provide correctness within the time frame of consensus in a chosen consensus protocol. The indexed merkle structure analyzed does not scale well because merkle roots on the blockchain cannot be updated and still have previous merkle verification work without at least log2(n) hashes (where n is leaf nodes in tree) sent to each node trying to validate the correctness of a transaction. This paper only explores theory and does not test the protocol. Sample code for IP indexed merkle trees: https://goo.gl/1DqDP3

@@

Proof of correctness has 3 parts: integrity, identity, and currentness. RPKI and BGPsec (when implemented) provide full integrity, full identity, and partial correctness. In BGPsec, there is a timestamp, however, it does not guarantee that a given routing update is the most recent one because updates can be withheld because of misconfigurations, new filters, or malicious ASes.

The explored blockchain is called Blockchain-Merkle BGP. Blockchain is used to create an ordering of routing tables and indexed merkle trees are used to conceal and ensure that routes are up-to-date. This paper shows that if merkle trees can adjust when some routing roots change, without resending the full merkle verification, then routing updates can be checked at any time efficiently against the ledger/blockchain for correctness.

\subsection{Shortcomings and Author’'s Note}

There are two shortcomings in this draft. First, the fact that BGP upgrades are so slow means that this protocol, even if fleshed out, would probably not ever be considered as an addition to BGP--the work is worthless if nearly worthless if only applicable to BGP. The goal in the future is see if similar ideas can be applied to the Bitcoin Lightning Network. Second, I (the author and researcher) am not confident in my ability to understand the severity of the data availability problem in BGP or any network relying on an external gateway protocol. I need guidance from an expert in BGP to (1) create a set of experiments to test the severity of data availability and (2) understand the current literature around data availability. Since it is one of the first iterations of this paper, I feel it is appropriate to add this disclaimer. I am much more confident in my understanding of blockchain than BGP. I am calling on those who are an expert in BGP to collaborate with me. Thank you.

@@

There are other attacks on blockchain: nothing at stake attack (for POS), sybil attacks, and quantum computers. Briefly, nothing at stake is the problem that block producers do not have any incentive to choose one block, and therefore, will mine after any block as long as they are confident that the blocks before the one they are mining will be accepted by the network. The worry is that miners will mine on top of forks in order to increase the likelihood of a payout, and this does not solve the double spend problem. Sybil attacks occur when malicious nodes cut of honest nodes from the network [Heilman 2015), but it is hard to successfully do if the P2P network is interconnected well (from good seeding). Quantum computers are only a problem if the signature algorithms that are used in transactions are based on the discrete log problem (RSA or ECC) because Shor’s algorithm makes it computationally feasible to factor large numbers (Shor 1994). Hash functions are not as vulnerable to quantum computers as signatures are because key sizes only have to be doubled.

@@

Now that there is an efficient tree the merkle root can be created. The tree is recursively hashed from bottom up. First, we must must make sure that every middle children has left and right siblings that are not None. Siblings are the other children of one’s parent. For each sibling slot that is none (for a middle node), we add a node with a data string ”LEFT” or ”RIGHT” because otherwise, middle node hashes could not be distinguished from left hashes if there are only right and middle children. Now the merkle root can be created with integrity of position of the leaf nodes. We start at the root node, find the root’s hash by hashing each of its children, which we get by hashing their children, and so on until a leaf node is reached (base case of recursive function) and then we backtrack.

@@

Another advantage of a centralized trusted authority is that many ASes already have connections with ICANN and a RIR to some degree because of RPKI. It is probably easier to convince ASes to add a connection to their RIR than join a p2p network. Further, a central authority can fix a bug faster than a consensus protocol, although it may take longer to find the bug there are less parties running the software than in a consensus protocol. The main disadvantage to a central authority is that there is single weak point. If the trusted authorities servers fail, there could be significant outages. This weakness can be mitigated through distributed and fault-tolerant computing. It is not clear whether an attack on an authority's servers is easier than the ripple consensus protocol (described in previous section) because ripple has a $>$20\% attack.
